Basic MODIS preparation in GRASS GIS

### 2011-01-05 tutorials/grass_modis/article_MODIS.tex
included MCD43B2 example
git-svn-id: https://svn.osgeo.org/grass/grass-promo@44878 15284696-431f-4ddb-bdfa-cd5b030d7da7

>>>>

In the case of BRDF\_Albedo\_Quality SDS (SDS\_BRDF), we may create an all BRDF levels inclusive mask with:

\begin{smallverbatim}
 r.mapcalc BRDFmask1=if(SDS_BRDF>1,null(),1)
\end{smallverbatim}

A more conservative version will be including only successful Full BRDF inversions:

\begin{smallverbatim}
 r.mapcalc BRDFmask2=if(SDS_BRDF>0,null(),1)
\end{smallverbatim}
